Diffantom: a software layer to build digital phantoms of whole-brain diffusion MRI

### 2015-06-18 paper/main.tex
finishing early version of paper

\noindent\textbf{\textit{Interpretation and use\textcolon}}
In order to release a reproducible dataset, along with an usable software to create custom data,
  we also distribute the software tools summarized in \autoref{fig:figure1}.

@@

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\linewidth]{figures/figure01}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:figure1} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
\end{figure}

>>>>

\noindent\textbf{\textit{Interpretation and use\textcolon}}
In order to release a reproducible dataset, along with an usable software to create custom data,
  we also distribute the software instrumentation presented in \autoref{fig:figure1}.

@@

\glsresetall

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\linewidth]{figures/figure01}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:figure1} Figure \arabic{figure}. }%
{\emph{Diffantom} is a software layer wrapping the \acrfull{hcp} datasets to generate whole-brain diffusion \gls*{dmri} data.
First, the tissue fraction maps $\{T_1, T_2, T_3\}$ are computed using FSL FAST \citep{zhang_segmentation_2001}.
Second, the fiber orientation maps $\{V_1, V_2, V_3\}$ and corresponding volume fraction maps $\{F_1, F_2, F_3\}$ are
  obtained using the Multi-Shell ball-and-stick model of BEDPOSTX \citep{jbabdi_modelbased_2012}.
The third step takes the fiber orientations $\{V_1, V_2, V_3\}$ and their weights $\{F_1, F_2, F_3\}$ to compute the
  corresponding \glspl{fod} using spherical convolution of the single fiber response with each fiber orientation at
  each voxel.
The resulting \glspl{fod} map is then combined with three isotropic compartments corresponding to $\{T_1, T_2, T'_3\}$
  before generating the signal using \emph{phantomas} \citep{caruyer_phantomas_2014}.
The fraction map $T'_3 = T_3 - \sum F_i$ is the remaining isotropic fraction across the \gls*{wm} tissue map.
Finally, data can be used to compute the whole-brain tractography, for instance.}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\linewidth]{figures/figure02}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:figure2} Figure \arabic{figure}. }%
{Fig 2 caption}
\end{figure}
